\textbf{Dynamic Transition Analysis with TIMES:}\\ I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions

### 2018-01-03 docs/poster.tex
fiddling with figure

\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes, calc }
% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]

\tikzstyle{const} = [rectangle, draw, text centered, fill=purple!20]
\tikzstyle{data} = [rectangle, draw, text centered, fill=green!20]

@@

\begin{block}{Methodology}
Multiple studies have been conducted to compare the impact of innovative energy technologies in different regions of the world using \textit{static} scenario analyses \cite{chyong_chi_dynamics_2009} \cite{feng_system_2013} \cite{kikuchi_simulation-based_2017} \cite{li_energy_2010} \cite{pambudi_impact_2017} \cite{pambudi_future_2016}. We will simulate \textit{dynamic transition scenarios} \cite{jebaraj_review_2006} \cite{pfenninger_energy_2014} , with realistic constraints and technology readiness of energy generation technologies (in terms of generation, transmission \& storage), aimed at minimizing carbon emissions. We will further extend previous work by combining multiple technologies in a single heterogeneous system.\\

The TIMES (The Integrated MARKAL-EFOM System) model generator \cite{loulou_documentation_2005} \cite{seebregts_energy/environmental_2002} optimizes energy systems of a model using linear and mixed-linear algorithms while implementing user-defined objective functions (such as minimizing carbon emissions or costs) within user defined constraints such as energy generation demand. It will be used to simulate near-term energy transitions while focusing on reduction of carbon emissions.

@@

This research is being performed using funding received
from the I\textsuperscript{2}CNER Programs under award number \textbf{<insert details here>}.

\begin{alertblock}{Contact Information}
\setbeamercolor{block title}{fg=norange,bg=white} % Change the block title color
\begin{itemize}

	\item Web: \href{arfc.github.io}{arfc.github.io}
	\item Email: \href{mailto:kdhuff@illinois.edu}{kdhuff@illinois.edu}
\end{itemize}

@@

\begin{figure}
	\centering
	\scalebox{1.0}{
		\begin{tikzpicture}[>=stealth,
		node distance=\figwidth,
		on grid,
		align=center,
		auto]
		% Place nodes
		\node [block] (times) {\textbf{TIMES Model Generator}};
		\node [cloud, below=\figwidth of times] (mod) {\texttt{MODEL} \\ heterogeneous \\ multi-technology \\ model of Japan};
                \node [cloud, above left=1.5\figwidth and 2*\figwidth of times] (dat) {\texttt{DATA}\\regarding\\both\\i$^2$cner\\ \&\\ conventional\\technologies};
                \node [data, above=1.5\figwidth of dat] (dat1) {Storage\\Capacity};
                \node [data, above=0.5\figwidth of dat1] (dat2) {Thermal\\Efficiency};
                \node [data, above=0.5\figwidth of dat2] (dat3) {Capacity\\factor};
                \node [data, above=0.5\figwidth of dat3] (dat4) {Availability\\factor};
                \node [data, right=\figwidth of dat1] (dat5) {Thermal\\capacity};
                \node [data, above=0.5\figwidth of dat5] (dat6) {Fuel costs};
                \node [data, above=0.5\figwidth of dat6] (dat7) {Construction\\costs};
                \node [data, above=0.5\figwidth of dat7] (dat8) {Operation\\costs};
                \node [data, above=0.5\figwidth of dat8] (dat9) {Maintenance\\costs};
                \node [data, right=\figwidth of dat5] (dat10) {Technology\\readiness};
                \node [data, above=0.5\figwidth of dat10] (dat11) {Construction\\time};
                \node [data, above=0.5\figwidth of dat11] (dat12) {Carbon\\intensity};
                \node [data, above=0.5\figwidth of dat12] (dat13) {Fuel needs};
		\node [cloud, above=\figwidth of times] (of) {\texttt{OBJECTIVE}\\\texttt{FUNCTION}};
		\node [block, above left=\figwidth of of] (min) {Minimize\\carbon emissions \\ from all sources};
		\node [block, above right=\figwidth of of] (max) {Maximize\\energy market\\ diversity};
		\node [cloud, above right=1.5*\figwidth and 2*\figwidth of times] (const) {\texttt{CONSTRAINTS} \\ e.g.: Deployed \\ sources must\\ meet energy \\ demand};
		\node [const, above=\figwidth of const ] (dem) {electricity\\demand growth};
        \begin{scope}[on background layer]
		\draw[->, ultra thick] let \p1=($(times)-(dat)$) in (dat) -- +(0,\y1)-- +(times);
		\draw[->, ultra thick] (of) -- (times);
		%\draw[->, ultra thick] let \p3=($(times)-(const)+(2,3)$),\p4=($(times)+(9,9)$),\p5=($(const)-(3,3)$) in (\x3,\y4) -- +(0,\y2)-- +(times);
		\draw[->, ultra thick] let \p2=($(times)-(const)$) in (const)-- +(0,\y2) -- + (times);
		\draw[->, ultra thick] (times) -- (mod);
		\draw[->, ultra thick] (min) -- (of);
		\draw[->, ultra thick] (max) -- (of);
		\draw[->, ultra thick] (dem) -- (const);
		\draw[->, ultra thick] (dat1) -- (dat);
		\draw[->, ultra thick] (dat2) -- (dat);
		\draw[->, ultra thick] (dat3) -- (dat);
		\draw[->, ultra thick] (dat4) -- (dat);
		\draw[->, ultra thick] (dat5) -- (dat);
		\draw[->, ultra thick] (dat6) -- (dat);
		\draw[->, ultra thick] (dat7) -- (dat);
		\draw[->, ultra thick] (dat8) -- (dat);
		\draw[->, ultra thick] (dat9) -- (dat);
		\draw[->, ultra thick] (dat10) -- (dat);
		\draw[->, ultra thick] (dat11) -- (dat);
		\draw[->, ultra thick] (dat12) -- (dat);
		\draw[->, ultra thick] (dat13) -- (dat);
               % \draw[out=330,in=300,looseness=8] (mod) -- (mod);
        \end{scope}
 \end{tikzpicture}
	}
	\caption{Basic methodology for dynamic simulation of Japan's energy system.}
\end{figure}

@@

\begin{block}{References}
        {\footnotesize\bibliographystyle{abbrv} 
        \bibliography{poster}}
\end{block}
\end{column} % End of the final column

>>>>

\usepackage{tikz}
\usetikzlibrary{arrows.meta}

\usetikzlibrary{positioning, arrows, decorations, shapes, calc }
% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]

\tikzstyle{const} = [rectangle, draw, text centered, fill=orange!20]
\tikzstyle{data} = [rectangle, draw, text centered, fill=green!20]

@@

\begin{block}{Introduction}
Previous work has compared the impact of innovative energy technologies in 
various world regions using \textbf{static} scenario analyses 
\cite{chyong_chi_dynamics_2009,feng_system_2013,kikuchi_simulation-based_2017,li_energy_2010,pambudi_impact_2017,pambudi_future_2016}.  
We will simulate \textbf{dynamic} transition scenarios 
\cite{jebaraj_review_2006,pfenninger_energy_2014} aimed at minimizing carbon 
emissions in Japan by 2050. These scenarios will include realistic constraints 
regarding technology readiness (in terms of generation, transmission \& 
storage) and will combine multiple technologies in a single heterogeneous 
system model.
\end{block}

\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function (such as minimizing carbon emissions or costs) is solve within user defined constraints such as energy generation demand.  
\end{block}

@@

@@

\begin{figure}
	\centering
	\scalebox{1.0}{
                \begin{tikzpicture}[>={Latex[width=6mm,length=6mm]}, 
                                node distance=\figwidth, 
                                on grid, 
                                align=center, 
                                auto]
		% Place nodes
		\node [block] (times) {\textbf{TIMES Model Generator}};
		\node [cloud, below=\figwidth of times] (mod) {\texttt{MODEL} \\ heterogeneous \\ multi-technology \\ model of Japan};
                \node [cloud, above left=1.5\figwidth and 2*\figwidth of times] 
                (dat) {\texttt{DATA}\\regarding both\\i$^2$cner and\\ conventional\\technologies};
                \node [data, above=1.5\figwidth of dat] (dat1) {Storage\\Capacity};
                \node [data, above=0.5\figwidth of dat1] (dat2) {Thermal\\Efficiency};
                \node [data, above=0.5\figwidth of dat2] (dat3) {Capacity\\factor};
                \node [data, above=0.5\figwidth of dat3] (dat4) {Availability\\factor};
                \node [data, right=\figwidth of dat1] (dat5) {Thermal\\capacity};
                \node [data, above=0.5\figwidth of dat5] (dat6) {Fuel costs};
                \node [data, above=0.5\figwidth of dat6] (dat7) {Construction\\costs};
                \node [data, above=0.5\figwidth of dat7] (dat8) {Operation\\costs};
                \node [data, above=0.5\figwidth of dat8] (dat9) {Maintenance\\costs};
                \node [data, right=\figwidth of dat5] (dat10) {Technology\\readiness};
                \node [data, above=0.5\figwidth of dat10] (dat11) {Construction\\time};
                \node [data, above=0.5\figwidth of dat11] (dat12) {Carbon\\intensity};
                \node [data, above=0.5\figwidth of dat12] (dat13) {Fuel needs};
		\node [cloud, above=\figwidth of times] (of) {\texttt{OBJECTIVE}\\\texttt{FUNCTION}};
		\node [block, above left=\figwidth of of] (min) {Minimize\\carbon emissions \\ from all sources};
		\node [block, above right=\figwidth of of] (max) {Maximize\\energy market\\ diversity};
		\node [cloud, above right=1.5*\figwidth and 2*\figwidth of times] (const) {\texttt{CONSTRAINTS} \\ e.g.: Deployed \\ sources must\\ meet energy \\ demand};
		\node [const, above=\figwidth of const ] (dem) {electricity\\demand growth};
		\node [const, left=\figwidth of dem ] (init) {initial\\condition (2010)};
		\node [const, above=0.5*\figwidth of dem] (infra) {infrastructure\\availability};
		\node [const, left=\figwidth of infra] (sec) {consumption\\by sector};
		\node [const, above=0.5*\figwidth of infra] (reg) {regional\\transmission};
        \begin{scope}[on background layer]
		\draw[->, ultra thick] let \p1=($(times)-(dat)$) in (dat) -- +(0,\y1)-- +(times);
		\draw[->, ultra thick] (of) -- (times);
		%\draw[->, ultra thick] let \p3=($(times)-(const)+(2,3)$),\p4=($(times)+(9,9)$),\p5=($(const)-(3,3)$) in (\x3,\y4) -- +(0,\y2)-- +(times);
		\draw[->, ultra thick] let \p2=($(times)-(const)$) in (const)-- +(0,\y2) -- + (times);
                \draw[->, ultra thick] (times) -- (mod);
		\draw[->, ultra thick] (min) -- (of);
		\draw[->, ultra thick] (max) -- (of);
		\draw[->, ultra thick] (dem) -- (const);
		\draw[->, ultra thick] (dat1) -- (dat);
		\draw[->, ultra thick] (dat2) -- (dat);
		\draw[->, ultra thick] (dat3) -- (dat);
		\draw[->, ultra thick] (dat4) -- (dat);
		\draw[->, ultra thick] (dat5) -- (dat);
		\draw[->, ultra thick] (dat6) -- (dat);
		\draw[->, ultra thick] (dat7) -- (dat);
		\draw[->, ultra thick] (dat8) -- (dat);
		\draw[->, ultra thick] (dat9) -- (dat);
		\draw[->, ultra thick] (dat10) -- (dat);
		\draw[->, ultra thick] (dat11) -- (dat);
		\draw[->, ultra thick] (dat12) -- (dat);
		\draw[->, ultra thick] (dat13) -- (dat);
		\draw[->, ultra thick] (reg) -- (const);
		\draw[->, ultra thick] (infra) -- (const);
		\draw[->, ultra thick] (sec) -- (const);
		\draw[->, ultra thick] (init) -- (const);
                \path[->] (mod) edge [ultra thick,out=330,in=0,looseness=10] (mod) node[above right=0.1\figwidth and 0.8\figwidth] {simulate\\2010-2050};
                %\draw (mod.east) to [->, ultra thick,looseness=10] (mod.south) node[above right=0.1\figwidth and 0.1\figwidth] {simulate\\2010-2050};
        \end{scope}
 \end{tikzpicture}
	}
	\caption{Basic methodology for dynamic simulation of Japan's energy system.}
\end{figure}

@@

\begin{block}{References}
        {\footnotesize\bibliographystyle{abbrv} 
        \bibliography{poster}}
\end{block}

\begin{alertblock}{Contact Information}
\begin{itemize}
	\item Web: \href{arfc.github.io}{arfc.github.io}
	\item Email: \href{mailto:kdhuff@illinois.edu}{kdhuff@illinois.edu}
\end{itemize}

This research is being performed using funding received
from the International Institute for Carbon Neutral Energy Research (I$^2$CNER) 
Initiative on Challenges in Energy Assessment and Energy Transitions at  the  
University of Illinois under Director Petros Sofronis.

\end{column} % End of the final column
